Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-02 snapshot_system/failover.tex
Updated graphs to the new versions.

\begin{figure}
    \centering
    \subfigure[Sharing of data under VM-oblivious dedup model]
    {
        \includegraphics[width=3in]{images/share_model_vc.pdf}
        \label{fig:share_vc}
    }
    \\
    \subfigure[Sharing of data under VM-centric dedup model]
    {
        \includegraphics[width=3in]{images/share_model_vo.pdf}
        \label{fig:share_vo}
    }
    \caption{Difference of sharing data under VO and VC approaches}
    \label{fig:share}
\end{figure}

@@

Figure~\ref{fig-vo-links} shows the average number of VMs sharing a block in
the global index as more VMs are added in VO.  The first 15 VMs are all windows
machines, so that explains the initial higher values, but for the most part the
average number of links is between 1.5 and 2. Figure~\ref{fig-vo-fsb-links}
shows the average number of VMs sharing a filesystem block (FSB) in the global
index, but only for the 15 windows machines (the last machine has a much larger
hard-drive, and therefore more unique data, which explains the drop-off in the
last datapoint).  This is a reasonable assumption, that a cluster will have one
OS dominating, and for our small dataset the number of links to an FSB
increases as more VMs of the same OS are added. You can see in the plot however
that even though a FSB contains 16K chunks, the average number of links to an
FSB is only several times the number of average links to a chunk. This is
because even in the VO global deduplication model, as long as writes are
batched a single FSB will tend to contain chunks from only a small number of
VMs. Below we show the significant impact the number of links has on VM backup
reliability.

>>>>

\begin{figure}
    \centering
    \subfigure[Sharing of data under VM-oblivious dedup model]
    {
        \includegraphics[width=3in]{images/share_vc.pdf}
        \label{fig:share_vc}
    }
    \\
    \subfigure[Sharing of data under VM-centric dedup model]
    {
        \includegraphics[width=3in]{images/share_vo.pdf}
        \label{fig:share_vo}
    }
    \caption{Difference of sharing data under VO and VC approaches}
    \label{fig:share}
\end{figure}

@@

Figure~\ref{fig-vo-links} shows the average number of VMs sharing a block in
the global index as more VMs are added in VO.  The first 15 VMs are all windows
machines, so that explains the initial higher values, but for the most part the
average number of links is between 1.5 and 2. Figure~\ref{fig-vo-fsb-links}
shows the average number of VMs sharing a filesystem block (FSB) in the global
The first 15 VMs added are all windows (though the last one has a much larger
hard drive which explains the drop after 14), which is why the number of block
links goes up quickly for the first half of the graph. You can see in the plot
that even though a FSB contains 16K chunks, the average number of links to an
FSB is only several times the number of average links to a chunk. This is
because even in the VO global deduplication model, as long as writes are
batched a single FSB will tend to contain chunks from only a small number of
VMs. Below we show the significant impact the number of links has on VM backup
reliability.
